---
title: "lab 5"
author: "Eli Schulman"
date: "10/25/2021"
output: 
  html_document: 
    toc: yes
    theme: cerulean
    # code_folding: hide
---
### Overview of Setup and Setting Changes
- settings > Output Options >
  - table of contents: includes links to the RMarkdown sections (based on number of #'s)
  - changed theme to cerulean
  - code_folding: enables collapsible code in the RMarkdown
  
### Lab Overview - Confidence Intervals
```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(effsize)
```

## Part 1: use 't.test()' to calculate confidence intervals

### Example 1: 
- single mock sample
- in-line code referencing
- t.test()

```{r}
# create mock sample
otter_len <- c(30, 40, 55, 27, 38, 36, 39, 60, 69, 17)

# find confidence interval
otter_ci <- t.test(otter_len)

# find sd
otter_sd <- sd(otter_len)

# interpreting confidence interval of (28,50): if we took a bunch of samples, we'd expect that 95% of them would contain the sample mean between 28 and 50.
```

#### use in-line reference to draw from the t.test() numbers. use  which makes the values in the text active
Mean otter length is `r round(otter_ci$estimate, 2)` inches with a 95% confidence interval of 
[`r signif(otter_ci$conf.int[1], 4)`, `r signif(otter_ci$conf.int[2], 4)`] inches.



### Example 2: 
- create mock sample and decide whether we can reject the null hypothesis (default null hypothesis is: these samples were drawn from populations with the same mean) (null hypotheses --> difference in means of population is equal to 0)
- p.val of .15 and means of 5 and 7 --> if these samples were taken from pops with the same mean, theres a 15% chance that the difference in means would be 2 (7-5).
- reject null hypothesis if p.val < .05

#### Two sample t-test
```{r}
oak_trees <- c(20, 19, 23, 25, 21, 16)
pine_trees <- c(30, 22, 27, 23, 35, 32)

tree_t_test <- t.test(oak_trees, pine_trees)

```

output with in-line texts: the mean height of oak and pine trees were (X +- Y) and (X +- Y), respectively. The difference was not significant (t(`r tree_t_test$parameter`) = `r round(tree_t_test$statistic, 1)`, p = `r round(tree_t_test$p.value, 2)`)

"two-sample t-test; t(df) = t-statistic, p=p.val"


